Storing messages with multipartite neural cliques

### 2014-06-25 Articles/article.tex
Tracé théorique + simulations + calculs
...

\documentclass[english,12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%

\title{Storing messages with neural multipartite cliques}
\author{L}
\date{
	}
%

@@

\theoremstyle{definition}
\newtheorem{theoreme}{Theorem}
\renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}

@@

	\maketitle%
	%\section*{Introduction}

@@

	The simulations agree with the analytical result.

@@

@@

	Marche un petit peu, mais pas forcément significatif : à tester plus en détail.

@@

	\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]

	\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]

	Sans tenir compte du choix au hasard si plus sont activés.
	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}

>>>>

\documentclass[english,11pt,twocolumn]{article}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

\title{Storing messages with multipartite neural cliques}
\author{???}
\date{
	}
%

@@

\theoremstyle{definition}
\newtheorem{theoreme}{Theorem}
\renewcommand{\thetheoreme}{\arabic{section}.\arabic{theoreme}}
\providecommand{\keywords}[1]{\textbf{Index terms---} #1}

@@

	\maketitle

	 \begin{abstract}
	 ???
	 \end{abstract}

	\keywords{associative memory, error correcting code}

	\section{Introduction}

	\section{Networks of neural cliques}

	\subsection{Learning messages}

		\subsection{Retrieving messages}

		\subsubsection{The "winner takes all" rule}

		\subsubsection{The "$a$ winners take all" rule}

		less biologically plausible rule

		same algorithmic complexity

	\section{Retrieval performance}

		\subsection{Analytical results}

@@

	The simulations agree with the analytical results for density and error rate.

@@

	\subsection{Simulations}
		Improves the retrieval rate for multiple iterations and/or corrupted messages.
	\begin{figure}
		\includegraphics[width=8.5cm]{densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
		\end{figure}

@@

@@

	% À corriger avec sommes multiparties
	%\[P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \]

	%\[P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a c_k} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}\]

	Sans tenir compte du choix au hasard si plus sont activés.

	\section{Conclusion}

	%Marche mieux pouur de petits c --> le faire sur le sparse ?
	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}
